Predicting the Quality of CDR-H3 Antibody Loop Structural Models

### 2022-12-16 paper.tex
Fixed table reference
Updates from Overleaf

\documentclass[12pt]{article}
\bibliographystyle{unsrt}
\usepackage{a4}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\newcommand{\ca}{\mbox{C$\alpha$}}
\newcommand{\VH}{\mbox{V\kern-.1667em \lower.5ex\hbox{\scriptsize H}}}
\newcommand{\VL}{\mbox{V\kern-.1667em \lower.5ex\hbox{\scriptsize L}}}
\newcommand{\VHVL}{\mbox{\VH/\VL}}
\newcommand{\CH}[1]{\mbox{C\lower.5ex\hbox{\scriptsize H}#1}}
\newcommand{\CL}{\mbox{C\kern-.0833em \lower.5ex\hbox{\scriptsize L}}}
\newcommand{\FV}{\mbox{\it Fv}}
\newcommand{\Fab}{\mbox{\it Fab}}

@@

\title{Predicting the Quality of CDRH3 Antibody Loop Structural Models}
\author{Lilian M.\ Denzler and Andrew C.R.\ Martin\\
Structural and Molecular Biology, Division of Biosciences,\\
University College of London,\\
Gower Street,\\
London WC1E 6BT, UK
}

@@

\begin{abstract}
  Therapeutic antibodies have shown an unprecedented pace of
  development and have brought new hope for the treatment of numerous
  diseases. Bioinformatics tools for modelling antibody structures
  have become invaluable for antibody engineering and the development
  of therapeutic antibodies. The antigen-binding site consists of six
  hypervariable loops, also known as the Complementary Determining
  Regions (CDRs), all of which can be modelled with adequate accuracy,
  except for one. It remains remarkably difficult to model the third CDR
  loop of the antibody heavy chain. CDR-H3 has
  far greater length and sequence variability, with such great structural
  diversity, that modelling it is considerably harder.

  Many approaches for antibody modelling, such as our
  abYmod software, have been developed. Although such efforts have
  improved prediction accuracy the results for CDR-H3 are
  still inconsistent and require further improvement. Providing a
  confidence score for the structure predictions would aid in
  differentiating well-modelled structures from incorrectly modelled
  structures, giving the abYmod user a clearer understanding of the
  generated 3D-model reliability.

@@

Antibodies are highly specialized proteins of the immune system that
are produced in response to a foreign substance, called an antigen. A
mature antibody binds a specific antigen with high affinity, while
only weakly interacting with other antigens, or not at all. This high affinity and high specificity sets them apart from other pharmaceuticals and makes them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.
Furthermore, in contrast with small drug molecules, antibodies can not
only bind pockets, but also flat, concave or convex
surfaces\cite{MacCallum1996}. Their unique characteristics have enabled 
researchers to develop efficient antibody drugs for treating cancers,
autoimmune disorders, infectious diseases and many more\cite{Lu2020}.
Four of the top 10 best-selling drugs in
2020 were monoclonal antibodies\cite{Urquhart2021}.

In order to design therapeutic antibodies rationally, knowledge of
their structure is essential. The acquired structural information can
be used to increase binding affinity to a target of interest,
predicting both the exact binding site and the antibody stability as
well as assessing immunogenicity\cite{Abhinandan2007}. As
experimental structure determination is costly and time
consuming, computational predictions of an antibody's structure are
used to streamline the process.

The variable
fragment (Fv) of an antibody contains the six complementarity determining regions
(CDRs, also known as hypervariable loops) which form the antigen binding site.
All except one of these loops can be clustered
into a limited number of `canonical structures'\cite{Al-Lazikani}. Therefore, modelling
these loops with adequate accuracy is commonly
achievable\cite{North2011}.  However, the CDR loop 3 of the 
heavy chain (CDR-H3) has a far greater sequence variability due to the
processes of V(D)J recombination and somatic hyper‐mutation and its
structure has remained unclassifiable\cite{Finn2016}. The variety in
structure is so great, that its structural diversity is remarkable
even compared to other protein loops\cite{Regep2017}. It was found
that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
structural neighbour, while 30\% of CDR-H3 loops have a
completely unique structure compared with under 3\% for all non-antibody
loops\cite{Regep2017}.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{AMA.eps}
  \caption {RMSD values of the CDR-H3 loop for structures from the
    Antibody Modelling Assessment I (2011) and AMAII (2014). abYmod
    outperforms other modelling software in some instances, but also
    has much lower accuracy in few outlier cases. Left: an abYmod
    structure for C705 could be generated, yet the RMSD calculation
    failed \lilian{Why? I'm sure we can resolve this!}.
    Right: Ab01 is the rabbit antibody PDB:4MA3, which was
    excluded in the CDR-H3 modelling stage in AMAII due to
    difficulties modelling the overall structure previously. Ab01 is
    shown for the methods, where generated 3D-models were adequate for
    RMSD calculation. \lilian{This needs better explanation}}
  \label{fig:AMA}
\end{figure}

@@

The RMSD values are also transformed into a set of binary values according to a
list of RMSD thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold). This is done so that binary ML-models can be
trained, which will predict the probability e.g.\ that the 3D-model's RMSD
is above 2\AA, 2.2\AA, 2.4\AA, and so on. The number of binary
classifiers incorporated into the first layer has a great effect on
the final ML-model, the general trend being that the more binary
classifiers are used, the better the nominal prediction. \lilian{Data?}

@@

Our ML-model was trained on different feature sets selected using manual
selection as well as algorithmic selection strategies (see methods), in order to
determine the most effective feature selection method. None of the
feature selection methods was a best fit for all ML-models. To create a ML-model implementing the encoding and feature selection strategies best suited for the specific ML-structure, a number of different combinations were tested, summarized in \ref{fig:results_table}.
\begin{table}[results_table]
    \centering
    \begin{tabular}{c|c}
         &  \\
         & 
    \end{tabular}
    \caption{Summary of Results of different ML-model implementations.}
    \label{tab:my_label}
\end{table}

\lilian{So, having read this, I have no idea what feature encoding you
  actually used, or where to find that information. What worked and
  what didn't? Where can I find a comparison of the performance?}

After the data were processed, they were used to train different
ML-models. Different types of ML-model were investigated, as the most
suited ML-model type has to be determined heuristically. 
The following list, which includes some of the most commonly used
algorithms, was used: logistic regression, linear discriminant analysis,
K-nearest neighbours classifier, decision tree classifier, Gaussian
NB, random forest classifier, support vector machine,
probability-based voting (also known as soft voting) and extreme
gradient boosting (XGBoost)\cite{Chen2016}.
\lilian{OK, but this is the Results section, so where are the results
  of using the different methods?}

@@

\subsection{Machine Learning Model Performance}
The overall best final ML-model was composed of several different binary
classifiers,\lilian{More detail!} with an extreme gradient boosting (XGBoost) top-layer
nominal classifier. Features were selected using random forest feature
selection.
\lilian{Explain how this works and which features were selected --- and how many?}
A final MCC\lilian{Explain how MCC is calculated over 3 classes} value of 0.99 could be achieved for an ML-model
using the abYmod log file \lilian{What parameters are actually used?} as input as well as the loop 3D-model file
itself. This value slightly dropped to 0.92 if no such log file was
given. This is mainly\lilian{is there anything else?} due to the fact that the template sequence
abYmod used to generate the 3D-model is unknown in the latter case.

\lilian{I'm not sure this is in the most logical place --- isn't this
  something that was chosen at the start? (At least in terms of
  telling the story}
The classifier predicts whether a 3D-model has an RMSD of below 2\AA,
between 2--4\AA, or above 4\AA. These cutoff values were selected
based on the observation that abYmod generally produces a 3D-model with
RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
be identified by screening for structures estimated to have an RMSD
above 4\AA. If a very high-quality 3D-model is needed one should also
exclude 3D-models with RMSD above 2\AA.

@@

@@

\subsubsection{Duplicate Screening}
Using AbDb's redundancy information it was ensured that no antibodies
were present in the dataset more than once. \highlight{The dataset was
  additionally screened for duplicate instances.}
\lilian{Did you find any? How was this screening done? It's far from trivial}

\subsubsection{Scaling}
Normalization and Standardization\lilian{What's the difference? Explain what they are.} were tested as scaling methods. Both
approaches are greatly influenced by outliers, and such datapoints are
ideally removed for optimal scaling. Here we define outliers as
datapoints that lie over 1.5 times the interquartile range (IQR) below
the first quartile or above the third quartile. The IQR is defined as
the range between quartile 1, i.e.\ the median of the lower half of the
data, and quartile 3, i.e.\ the median of the upper half of the
data. However, across all features there are a total of 632 outlier
values and removing such a large number of datapoints is not a viable
option. A robust scaler\cite{XXXX} was also used, which uses statistics that are
robust to outliers. The median is set to zero and numerical features
are scaled to the interquartile range.

@@

\subsection{Feature Calculations}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{feature_table.eps}
  \caption {A summary of how different feature values were calculated. \lilian{It's a table! Why import it?}}
  \label{fig:feature_table}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{angle.eps}
  \caption {Diagram \lilian{Needs a much simpler cartoon diagram --- it's difficult to see anything from this!}
    visualizing the process underlying the protrusion
    calculation. First, the base residues (i.e.\ H95 and H102, shown as
    red spheres) of the CDR-H3 (shown in red) are identified. Then, a
    line is drawn between the two \ca\ atoms of these residues (yellow
    dashed line). The distance of the \ca-atom of each residue in the
    CDR-H3 loop to this line is calculated. The residue which has the
    greatest distance to the line (shown as green sphere) is output
    as one-letter amino acid code and used as feature. The distance in
    \AA\ (depicted as yellow arrow) is used as the `protrusion'
    feature. \lilian{It's unclear whether you use both distance and amino acid, or just one of these.}}
  \label{fig:angle}
\end{figure}

\section{Discussion}
The results suggest that our classifier can differentiate
between well-modelled and less well-modelled CDR-H3 loop
structures. An MCC value of 0.99 was achieved, which underlines this
ability for accurate discrimination. Different methods for data
pre-processing, feature encoding, feature selection and hyperparameter
optimization were tested.
Feature encoding methods that were very high-dimensional
(one-hot-encoding, BLOSUM62, NLF) were found to be
unfavourable. Dimensionality reduction methods (Principal Component
Analysis (PCA), Independent Component Analysis (ICA), projection-based
methods e.g.\ t-SNE) were used on BLOSUM62 encoded matrices, which lead
to significant improvement. However, a physicochemical encoding
strategy was most effective.
The selection of features incorporated in the training set seemed to
be most important for effective learning. A multitude of methods were
tested. No one fit-for-all method for the different ML-models could be
found.\lilian{I'm not sure what this means.} However, for our top-layer classifier in our final ML-model
recursive feature elimination worked best.
A set of commonly used machine learning algorithms were tested, and
the best ML-models were incorporated into the final ensemble ML-model. A
stacked ML-model approach (consisting of 23 binary classifiers and a
single top-layer nominal classifier) was shown to outperform single
ML-models.
An MCC value of 0.99 was achieved for a classifier predicting whether
an input 3D-model has an RMSD value below 2\AA, 2\AA--4\AA\ or above
4\AA.

@@

\highlight{In a future research project residue patterns in correlation with RMSD
may be analyzed. Possibly, one might identify certain sequence
patterns that make accurate modelling with abYmod more
difficult. Furthermore, separate classifiers according to loop length
can be built. Given that loop length is the most important determinant
of 3D-model quality, this approach may yield some insight into the
challenges of modelling shorter \emph{vs.} longer loops.
One could also conduct an analysis of the predictor's behaviour when
abYmod is forced to use LoopDB-based modelling. This might shed light
on whether the ML-model presented in this paper is biased towards
abYmod's used source of template structures. It would also give an
indication of how well the predictor would work in combination with
other modelling software.}\lilian{We don't really need this, but can we see any trends from the feature selection?}

\lilian{We need a concluding paragraph relating back to the
  introduction and what this contributes to improvements in using
  antibody models.}

>>>>

\documentclass[12pt]{article}
\bibliographystyle{unsrt}
\usepackage{a4}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\usepackage{tabularx} 
\setlength\extrarowheight{2pt} % make the tables look less cramped
\usepackage{graphicx}
\usepackage{adjustbox}
\newcommand{\ca}{\mbox{C$\alpha$}}
\newcommand{\VH}{\mbox{V\kern-.1667em \lower.5ex\hbox{\scriptsize H}}}
\newcommand{\VL}{\mbox{V\kern-.1667em \lower.5ex\hbox{\scriptsize L}}}
\newcommand{\VHVL}{\mbox{\VH/\VL}}
\newcommand{\CH}[1]{\mbox{C\lower.5ex\hbox{\scriptsize H}#1}}
\newcommand{\CL}{\mbox{C\kern-.0833em \lower.5ex\hbox{\scriptsize L}}}
\newcommand{\FV}{\mbox{\it Fv}}
\newcommand{\Fab}{\mbox{\it Fab}}

@@

\title{Predicting the Quality of CDR-H3 Antibody Loop Structural Models}
\author{Lilian M.\ Denzler and Andrew C.R.\ Martin\\
Institute of Structural and Molecular Biology, Division of Biosciences,\\
University College of London,\\
Gower Street,\\
London WC1E 6BT, UK
}

@@

\begin{abstract}
  Therapeutic antibodies have shown an unprecedented pace of
  development and have brought new hope for the treatment of numerous
  diseases. Bioinformatics tools for modelling antibody structures
  have become invaluable for antibody engineering and the development
  of therapeutic antibodies. The antigen-binding site consists of six
  hypervariable loops, also known as the Complementary Determining
  Regions (CDRs), all of which can be modelled with high accuracy,
  except for CDR-H3, which generally has
  far greater length and sequence variability, with such great structural
  diversity, that modelling it is considerably harder.

  Many approaches for antibody modelling, such as our
  abYmod software, have been developed. Although such efforts have
  improved prediction accuracy, the results for CDR-H3 are
  still inconsistent and require further improvement. Providing a
  confidence score for the structure predictions would aid in
  differentiating well-modelled structures from incorrectly modelled
  structures, giving the abYmod user a clearer understanding of the
  generated 3D-model reliability.

@@

Antibodies are highly specialized proteins of the immune system that
are produced in response to a foreign substance, called an antigen. A
mature antibody binds a specific antigen with high affinity and specificity. This sets them apart from other pharmaceuticals and makes them effective drugs with endless possibilities in application given their ability to target an immense variety of antigens.
In contrast with small drug molecules, antibodies can not
only bind pockets, but also flat, concave or convex
surfaces\cite{MacCallum1996}. Their unique characteristics have enabled 
researchers to develop efficient antibody drugs for treating cancers,
autoimmune disorders, infectious diseases and many more\cite{Lu2020}.
Four of the top 10 best-selling drugs in
2020 were monoclonal antibodies\cite{Urquhart2021}.

In order to design therapeutic antibodies rationally, knowledge of
their structure is essential. The acquired structural information can
be used to modify binding affinity to a target of interest,
predicting both the exact binding site and the antibody stability as
well as assessing immunogenicity\cite{Abhinandan2007}. As
experimental structure determination is costly and time
consuming, computational predictions of an antibody's structure are
used to streamline the process.

The variable
fragment (Fv) of an antibody contains the six complementarity determining regions
(CDRs, also known as hypervariable loops) which form the antigen binding site.
All except one of these loops can be clustered
into a limited number of `canonical structures'\cite{Al-Lazikani}. Therefore, modelling
these loops with adequate accuracy is commonly
achievable\cite{North2011}.  However, the CDR loop 3 of the 
heavy chain (CDR-H3) has a far greater sequence and length variability due to the
processes of V(D)J recombination and somatic hyper‐mutation and its
structure has remained unclassifiable\cite{Finn2016}. The variety in
structure is so great, that its structural diversity is remarkable
even compared to other protein loops\cite{Regep2017}. It was found
that over 75\% of CDR-H3 loops do not have a sub-{\AA}ngstr\"{o}m non-antibody
structural neighbour, while 30\% of CDR-H3 loops have a
completely unique structure compared with under 3\% for all non-antibody
loops\cite{Regep2017}.

@@

The classifier predicts whether a 3D-model has an RMSD of below 2\AA,
between 2--4\AA, or above 4\AA. These cutoff values were selected
based on the observation that abYmod generally produces a 3D-model with
RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
be identified by screening for structures estimated to have an RMSD
above 4\AA. If a very high-quality 3D-model is needed one should also
exclude 3D-models with RMSD above 2\AA.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{AMA.eps}
  \caption {RMSD values of the CDR-H3 loop for structures from the
    Antibody Modelling Assessment I (2011) and AMAII (2014). abYmod
    outperforms other modelling software in some instances, but also
    has much lower accuracy in few outlier cases. 
    Right: Ab01 is the rabbit antibody PDB:4MA3, which was
    excluded in the CDR-H3 modelling stage in AMAII due to
    difficulties modelling the overall structure previously. Ab01 is
    shown for the methods, where generated 3D-models were adequate for
    RMSD calculation.}
  \label{fig:AMA}
\end{figure}

@@

The RMSD values are also transformed into a set of binary values according to a
list of RMSD thresholds (i.e. a 1 is assigned to above and 0 to below a given threshold). This is done so that binary ML-models can be
trained, which will predict the probability e.g.\ that the 3D-model's RMSD
is above 2\AA, 2.2\AA, 2.4\AA, and so on. The number of binary
classifiers incorporated into the first layer has a great effect on
the final ML-model, the general trend being that the more binary
classifiers are used, the better the nominal prediction.

@@

Our ML-model was trained on different feature sets selected using manual
selection as well as algorithmic selection strategies (see methods), in order to
determine the most effective feature selection method. None of the
feature selection methods was a best fit for all ML-models. To create a ML-model implementing the encoding and feature selection strategies best suited for the specific ML-structure, a number of different combinations were tested, summarized in \ref{fig:results_table}. Additional ML-Models were discarded due to poor performance. 
\begin{table}[]
\fontsize{12}{16}\selectfont
  \centering
  \caption{Summary of Machine-Learning Classifier Performances}
  \label{my-label}

  \begin{adjustbox}{width=\textwidth}

    \begin{tabularx}{\linewidth}{
    |>{\hsize=.35\hsize}X|% 10% of 4\hsize 
    >{\hsize=.4\hsize}X|% 30% of 4\hsize
    >{\hsize=.4\hsize}X|% 30% of 4\hsize 
    >{\hsize=.4\hsize}X|% 30% of 4\hsize
    >{\hsize=.4\hsize}X|% 30% of 4\hsize 
    >{\hsize=.4\hsize}X|% 30% of 4\hsize
    >{\hsize=.2\hsize}X|% 30% of 4\hsize
       % sum=4.0\hsize for 4 columns
  }
\hline
Features & Feature Selection Method & Optimi-zation Method& Multi/ Single-layer & First-layer weighted &Classifier Type & MCC\\
\hline
Basic & None & None & single & No & SVC & 0.54\\
Basic & None & Genetic Algorithm & single & No & SVC & 0.54 \\
All & None & None & single& No & Random Forest & 0.58\\
Selected & random forest feature selection & Genetic Algorithm & Single& No & Soft Voting & 0.59 \\
Selected & random forest feature selection & Genetic Algorithm & Multi& Yes & XGB & 0.63 \\
Selected & recursive feature elimination & Genetic Algorithm & Multi& Yes & XGB & 0.79 \\
Selected & recursive feature elimination & Genetic Algorithm & Multi& Yes & Decision-Tree & 0.99 \\
Selected (no log-file features) & recursive feature elimination & Genetic Algorithm & Multi& Yes & Voting(soft) & 0.92 \\
\hline
    \end{tabularx}

  \end{adjustbox}

\end{table}
\caption{table caption}

After the data were processed, they were used to train different
ML-models. Different types of ML-model were investigated, as the most
suited ML-model type has to be determined heuristically. 
The following list, which includes some of the most commonly used
algorithms, was used: logistic regression, linear discriminant analysis,
K-nearest neighbours classifier, decision tree classifier, Gaussian
NB, random forest classifier, support vector machine,
probability-based voting (also known as soft voting) and extreme
gradient boosting (XGBoost)\cite{Chen2016}.

@@

\subsection{Machine Learning Model Performance}
The overall best final ML-model was composed of several different binary
classifiers, \ref{fig:flow} with an extreme gradient boosting (XGBoost) top-layer
nominal classifier. Features were selected using a recursive feature elimination algorithm, through which a the weakest feature is removed recursively and the model performance is tested. In the final model 9 features are included: in the final model, the following features were included: tip\_pos, protrusion, length, total\_charge, nr\_charged, identity, similarity, Hydropathy and Hydropathy\_diff \ref{fig:feature_table}.

A final MCC value of 0.99 could be achieved for an ML-model
using the abYmod log file as input as well as the loop 3D-model file
itself. This value slightly dropped to 0.92 if no such log file was
given. This is due to the fact that the template sequence
abYmod used to generate the 3D-model is unknown in the latter case.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{flowchart_qualiloop.eps}
  \caption {Simplified pipeline for creating the final machine learning model that will predict 3D-model quality by giving its RMSD range.}
  \label{fig:flow}
\end{figure}

@@

\subsubsection{Duplicate Screening}
Using AbDb's redundancy information it was ensured that no antibodies
were present in the dataset more than once.

\subsubsection{Scaling}
Normalization and Standardization were tested as scaling methods. In normalization the range of the data is fixed between 0 and 1, while in Standardization the data is re-scaled to fit a Gaussian distribution. Both
approaches are greatly influenced by outliers, and such datapoints are
ideally removed for optimal scaling. Here we define outliers as
datapoints that lie over 1.5 times the interquartile range (IQR) below
the first quartile or above the third quartile. The IQR is defined as
the range between quartile 1, i.e.\ the median of the lower half of the
data, and quartile 3, i.e.\ the median of the upper half of the
data. However, across all features there are a total of 632 outlier
values and removing such a large number of datapoints is not a viable
option. A robust scaler\cite{XXXX} was also used, which uses statistics that are
robust to outliers. The median is set to zero and numerical features
are scaled to the interquartile range.

@@

\subsection{Feature Calculations}

\begin{table}[]
  \centering
  \caption{A summary of how different feature values were calculated.}
  \label{fig:feature_table}

  \begin{adjustbox}{width=\textwidth}

    \begin{tabular}{| m{5em} | m{20em}| m{20em} |}
    \hline
Feature Name & Description & method of Calculation \\
\hline
\hline
Sequence & Amino acid sequence of the CDR-H3 loop. & Sequence is given in one-letter amino acid codes.\\
\hline
Length & Number of residues in the CDRH3-loop, which is located at residues H95-H102. & The number of residues are counted.\\
\hline
Sequence Identity & Sequence identity of selected template (SeqA) with input loop sequence (SeqB) is determined after sequence alignment. Calculated by abYmod during modelling. & $Identity(SeqA,SeqB) = 100\%\frac{identical residues}{length(alignment)}$\\
\hline
Sequence similarity & Sequence similarity of selected template (SeqA) with input loop sequence (SeqB) is determined after sequence alignment. Calculated by abYmod during modelling. Similar residues are residues that have undergone conservative substitution. &
$Similarity(SeqA,SeqB) = 100\%\frac{identical residues+similar residues}{length(alignment)}$\\
\hline
Loop Protrusion & Distance of loop residue further away from the loop base & Geometrical calculations \protect\ref{fig:loopdist} \\
\hline
Protruding residue & The Amino acid code of the most protruding loop residue & Using the previously determined point furthest away from the loop base, the residue at this coordinate is determined and given as a one-letter amino acid code.\\
\hline
Charge & Total charge of the loop & Sum of charges of all residues in loop \\
\hline
Charge difference & Difference in total charge compared to template sequence & Difference between the two summed changes \\
\hline
Hydrophobicity & Mean Hydrophobicity values of loop & Based on Eisenberg consensus values\\
\hline
Hydrophobicity  difference & Sum of absolute differences between loop sequence and template loop& Based on Eisenberg consensus values\\
\hline
Accessibility & Total and average accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
\hline
Side-chain Accessibility & Total and average side-chain accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
\hline
Relative Accessibility & Total and average relative accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
\hline
relative side-chain Accessibility & Total and average relative side-chain accessibility for the loop& lee-Richards method implemented using the pdbsolv method from the BiopTools library.\\
\hline
Happiness & Happiness score, taking accessibility and hydropobicity into account. If a residue is 'happy' it will not be a buried hydrophilic or a surface hydrophobic residue. & Hydrophobicity values (see above) are normalized to a range of -1 to +1. Mean accessibility values are calculated as above. If hydrophobicity of loop is $<0$:
$Happiness = 1+Hydrophobicity(1-Accessibility)$
Otherwise:
$Happiness = 1-(Hydrophobicity Accessibility)$\\
\hline
Nr. of Contacts & Nr of contacts made by the residue of the loop within a range of 3.5\AA. Includes mainchain as well as sidechain atoms. Contacts made with residue within and outside of the loop are counted separately and as total. The ratio of inside vs outside is also calculated. & Modified version of the rangecontacts method in the BiopTools library. \\
\hline
Energy & Potential energy of the model. & Calculated by Gromacs during energy minimization step in abYmod modelling. \\
\hline
Lowest BLOSUM 62 Scoring Residue Pair & Each possible residue pair in the CDR-H3loop is scored by their BLOSUM 62 score. The lowest scoring pair's BLOSUM62 value will be combined with their residue separation to form the metric. & With separation being hte nuber of residues between the worst residue pair, and the worst score being the lowest BLOSUM62 score achieved by a residue pair, the metric is calculated as follows: $WorstBLOSUM = -log_2(separation)(worst score)$
\hline

    \end{tabular}

  \end{adjustbox}

\end{table}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{protrusion.eps}
  \caption {Diagram
    visualizing the process underlying the protrusion
    calculation. First, the base residues (i.e.\ H95 and H102, shown as
    red spheres) of the CDR-H3 (grey circles) are identified. Then, a
    line is drawn between the two \ca\ atoms of these residues.
    The distance of the \ca-atom of each residue in the
    CDR-H3 loop to this line is calculated (d). The residue which has the
    greatest distance to the line is output
    as one-letter amino acid code and used as feature. The distance d in
    \AA\is used as the `protrusion'
    feature.}
  \label{fig:angle}
\end{figure}

\section{Discussion}
The results suggest that our classifier can differentiate
between well-modelled and less well-modelled CDR-H3 loop
structures. An MCC value of 0.99 was achieved, which underlines this
ability for accurate discrimination. Different methods for data
pre-processing, feature encoding, feature selection and hyperparameter
optimization were tested.
Feature encoding methods that were very high-dimensional
(one-hot-encoding, BLOSUM62, NLF) were found to be
unfavourable. Dimensionality reduction methods (Principal Component
Analysis (PCA), Independent Component Analysis (ICA), projection-based
methods e.g.\ t-SNE) were used on BLOSUM62 encoded matrices, which lead
to significant improvement. However, a physicochemical encoding
strategy was most effective.
The selection of features incorporated in the training set seemed to
be most important for effective learning. A multitude of methods were
tested. No one fit-for-all method for the different ML-models could be
found. However, for our top-layer classifier in our final ML-model
recursive feature elimination worked best.
A set of commonly used machine learning algorithms were tested, and
the best ML-models were incorporated into the final ensemble ML-model. A
stacked ML-model approach (consisting of 23 binary classifiers and a
single top-layer nominal classifier) was shown to outperform single
ML-models.
An MCC value of 0.99 was achieved for a classifier predicting whether
an input 3D-model has an RMSD value below 2\AA, 2\AA--4\AA\ or above
4\AA.

@@
